%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
% Modified for the use of Wesley Nguyen.
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Wesley Nguyen} \\ \vspace{1pt}\href{https://wesngu28.com}{\raisebox{-0.2\height}\faUser\ \underline{wesngu28.com}} {\raisebox{-0.2\height}\faEnvelope\  \underline{wesngu028@gmail.com}} ~
    \href{https://linkedin.com/in/wesngu28/}{\raisebox{-0.2\height}\faLinkedin\ \underline{/in/wesngu28}}  ~
    \href{https://github.com/wesngu28}{\raisebox{-0.2\height}\faGithub\ \underline{wesngu28}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Sep. 2019 -- June 2023}
      {Geography: Data Science}{Seattle, Washington}
      { \footnotesize{\newline{}\textit{{Courses:}} GIS Database and Programming, GIS Data Management, Digital Geographies, Advanced Digital Geographies, Geographic Information and Spatial Analysis, Geographic Information Systems Workshop, Elements of Statistical Methods, Data Science Foundations Introduction to Machine Learning, Web Programming, Data Structures and Algorithms }}
    \resumeSubheading
      {Bellevue College}{Sep. 2017 -- June 2019}
      {Running Start}{Bellevue, Washington}
      { \footnotesize{\newline{}\textit{{Courses:}} Computer Programming I and II }}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {International Wood Products}{July 2022 -- September 2022}
      {Information Technology Intern}{Clackamas, Oregon}
      \resumeItemListStart
        \resumeItem{Aided in the preparation of company server, networking and technology equipment for company and employee use.}
        \resumeItem{Supported Microsoft 365 Enterprise and ERP systems, email servers, and operations for users across states.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon Fresh}{May 2021 -- July 2022}
      {Overnight Associate}{Bellevue, Washington}

    \resumeSubheading
      {Target Corporation}{October 2020 -- January 2021}
      {Fulfillment Expert}{Renton, Washington}

    \resumeSubheading
      {Newport Hills Swim and Tennis Club}{March 2018 -- November 2020}
      {Lifeguard}{Bellevue, Washington}
   
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://wesngu28.com}{wesngu28.com}} $|$ \emph{React, Next.js, Typescript, Mapbox, Tailwind}}{September 2022 - October 2022}
          \resumeItemListStart
            \resumeItem{Personal website to showcase my projects and practice more React.}
            \resumeItem{Features custom scrollytelling and a detailed about me. Hosted on custom domain.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://observatories.vercel.app/}{Observatory}} $|$ \emph{React, Next.js, Typescript}}{October 2022}
          \resumeItemListStart
            \resumeItem{Web app that is the interface for a CLI I made to read python and javascript dependency files.}
            \resumeItem{Displays a table of repositories not yet starred and allows the user to view information and star them.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://searchifyy.vercel.app/}{Searchify}} $|$ \emph{React, Next.js, Flask}}{March 2022 - August 2022}
          \resumeItemListStart
            \resumeItem{Web app to visualize user Spotify data, albums, playlists, tracks, and artists through tables and graphics.}
            \resumeItem{Connects to a Flask API backend which uses Pandas and various libraries to manipulate data from Spotipy, Spotify's python library for their API.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://wesngu28.github.io/mapping-terrorism/}{Mapping Terrorism}} $|$ \emph{Mapbox, JavaScript, Sass}}{April 2022 - June 2022}
          \resumeItemListStart
            \resumeItem{Web map built with the Mapbox JS library to visualize the data within the University of Maryland's Global Terrorism Dashboard.}
            \resumeItem{Implemented much of the html and css, as well as the map label and symbology for each individual point.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{United States Vacant Housing Analysis} $|$ \emph{Jupyter, Python, ArcGIS, SPSS}}{April 2022 - June 2022}
          \resumeItemListStart
            \resumeItem{Worked with a team in partnership with the United States Department of Urban Housing and Development to update a typology on vacant housing in the United States based on an earlier report by Raven Molloy in 2016. Processed data from the USPS, American Community Survey, Census Bureau, and NHGIS using Pandas.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{RhodesAPI and Closure} $|$ \emph{Typescript, Express, NodeJS, Docker}}{June 2022}
          \resumeItemListStart
            \resumeItem{Created a RESTFUL API for the mobile gacha tower defense game Arknights that supports GET, POST, and PUT endpoints. Uses a web scraper which stores the data in a MongoDB collection hosted on Atlas, cached with Redis.}
            \resumeItem{Created a Discord bot to use this api using Typescript and Discord.js, hosted in a Docker container.}
            \resumeItem{Wrote a suite of scripts to scrape YouTube channels for their live status, independent of the official YouTube API.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}



%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: HTML, CSS, Javascript, Typescript, Python, R, SQL, Bash, Java, LaTeX} \\
     \textbf{Tools}{: Windows, Linux (Debian, openSuse Tumbleweed), VS Code, Docker, Jest, Jupyter, Git} \\
     \textbf{Technologies}{: PostgreSQL, MongoDB, Redis, Bootstrap, Sass, Tailwind, React, Svelte, Vue, Next.js, Vite, Express, NodeJS, Flask, Markdown, ArcGIS, QGIS} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\begin{center}
    \tiny Updated - October 18th 2022
\end{center}

\end{document}
Footer